\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-12pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{1pt}
    \small +1 (289) 788-8260 $|$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $|$ 
    \href{https://www.linkedin.com/in/suleyman-kiani/}{\underline{linkedin.com/in/suleyman-kiani/}} $|$
    \href{https://github.com/kianis4}{\underline{github.com/kianis4}} $|$
    \href{https://www.suleyman.io/about}
    {\underline{suleyman.io/}}
\end{center}


%-----------EDUCATION-----------
\section{Education \& Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science in \textbf{Computer Science} (CO-OP)}{Nov 2024}

      \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Languages}{: JavaScript, TypeScript, Python, Java, C/C++, C\#, Ruby, HTML/CSS, SQL, Bash, Scala, PHP} \\  
        \textbf{Frameworks}{: React, Next.js, Django, Flask, Express, Ruby on Rails, Spring Boot, Angular, Helm, Prometheus} \\  
        \textbf{DevOps Tools}{: Linux, Docker, Bitbucket, Kubernetes, Terraform, GitHub Actions, Jenkins, CI/CD Pipelines} \\  
        \textbf{Libraries}{: Pandas, NumPy, GraphQL, Puppeteer, Axios, Selenium, JUnit, Jest, Mocha, Chai} \\  
        \textbf{Cloud Services}{: AWS (Lambda, EC2, S3, RDS, Kubernetes, DynamoDB, CloudFront, IAM), Azure, GCP} \\
        \textbf{Databases}{: PostgreSQL, MySQL, NoSQL, MongoDB, DynamoDB, Redis, Firebase, Cassandra} \\
    }}
\end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------

\section{Experience}
  \resumeSubHeadingListStart
          \resumeSubheading
          {Software \& IT Systems Lead }{August 2024 -- Present}
          {Burlington Training Centre}{Burlington, ON, Canada}
          \resumeItemListStart
            \resumeItem{\textbf{Architected and Implemented} a modern frontend using \textbf{Next.js}, \textbf{TypeScript}, and \textbf{Node.js}, integrating \textbf{RESTful APIs} to optimize user experience, resulting in a \textbf{20\% increase} in operational efficiency.}
            \resumeItem{\textbf{Developed and Migrated} legacy systems from ABC Financial to \textbf{Square} and \textbf{Chargify}, automating payment processes and increasing gym revenue by \textbf{\$50,000 annually} due to reduced platform fees.}
            % \resumeItem{\textbf{Designed and Deployed} a robust cloud-based infrastructure on \textbf{AWS}, improving system reliability and scalability by \textbf{40\%}, supporting increased user traffic with zero downtime.}
            \resumeItem{\textbf{Led Development} of internal tools for class scheduling, student tracking, and payment processing, using \textbf{React} and \textbf{SQL}, reducing manual overhead by \textbf{30 hours/month}. \textbf{SEO Optimization} \& enhanced website performance, achieving \textbf{Top 5 search rankings} for targeted local keywords and increasing traffic by \textbf{25\%} within six months.}
                  \resumeItem{
        \textbf{Created Automated Review Service} leveraging \textbf{AWS Lambda}, \textbf{RDS}, and \textbf{SNS}. Automated parsing of client appointment data, populating an \textbf{RDS database}, and triggering personalized review requests. Increased positive review rates by \textbf{30\%} while reducing negative feedback visibility by routing subpar reviews for internal review.
      }
            
          \resumeItemListEnd
    \resumeSubheading
      {Junior Web Developer (Co-op)}{May 2021 -- August 2022}
      {Giftcash, Inc.}{Remote, Hamilton, Canada}
      \resumeItemListStart
        \resumeItem{Contributed to the migration of a legacy \textbf{Python Django} monolithic backend to a modern, scalable \textbf{TypeScript Node.js serverless microservices architecture} achieving a \textbf{15\% increase in system scalability}.}

        \resumeItem{Optimized \textbf{PostgreSQL API} performance by designing efficient database indexes, refining query execution strategies, and integrating caching mechanisms, resulting in a \textbf{20\% reduction in response times}. Conducted performance analysis to identify bottlenecks, boosting API throughput under high-traffic scenarios.}

        \resumeItem{Automated data extraction workflows in \textbf{Agile} development environment by developing \textbf{Puppeteer} and \textbf{Axios} web scrapers to query company websites for gift card balance verification, boosting operational efficiency \textbf{25\%}.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS & LEADERSHIP-----------
\section{Projects \& Leadership}
\resumeSubHeadingListStart

% E&S Solutions
% \resumeProjectHeading
%     {\textbf{\href{https://www.es-soln.com/}{E\&S Solutions}} $|$ \emph{AWS (S3, Lambda, Cloudfront), SwiftUI, React}}{June 2023 -- Present}
%     \resumeItemListStart
%         \resumeItem{Co-founded a software services company delivering customized solutions to small businesses, specializing in automation and cloud-native solutions.}
%         \resumeItem{Automated client Google review requests using \textbf{AWS Lambda, SNS, S3}, and other cloud tools, reducing manual follow-up time by over 70\%.}
%         % \resumeItem{Developed \textbf{\href{https://github.com/E-S-Solutions/ProgressiveOverloadApp}{Overload Pro}}, an iOS app for fitness tracking and portfolio management, using \textbf{SwiftUI}, enabling personalized goal tracking for 100+ users.}
%     \resumeItemListEnd

% SKompXcel Academic Solutions
\resumeProjectHeading
{\textbf{\href{https://www.skompxcel.com/}{SKompXcel Academic Solutions}} $|$ \emph{Google Cloud, Systems Design, Mentorship}}{January 2024 - Present}
    \resumeItemListStart
        \resumeItem{Founded an academic tutoring and mentorship platform, providing personalized learning for students in Computer Science, Math, and Software Engineering. Mentoring students on topics such as algorithms, systems design, code review, and mock technical interviews, resulting in 80\% of students achieving their academic goals.}
        \resumeItem{Managed \textbf{Google Cloud} resources, including Compute Engine $\&$ Cloud Storage, to improve platform performance, automate scheduling workflows, and streamline contractor operations, boosting reliability and scalability.}


    \resumeItemListEnd
% E&S Solutions
\resumeProjectHeading
{\textbf{\href{https://www.skompxcel.com/}{E\&S Solutions}} $|$ \emph{AWS (S3, Lambda, CloudFront, RDS, EC2), Next.js, React}}{May 2023 - Present}
    \resumeItemListStart
        \resumeItem{Co-founded software services company delivering cloud-native solutions, automation, and full-stack applications for small businesses. Automated workflows via \textbf{Linux Bash \& Python scripts}, reducing manual aggregation \textbf{80\%}}
        \resumeItem{Developed \textbf{10+ Next.js/React} apps on Vercel \& AWS, leveraging \textbf{S3, CloudFront}, and \textbf{Route 53} for scalable web solutions with \textbf{Express.js} backends. Improved load times by \textbf{30\%} and reduced deployment overhead \textbf{50\%}.}
    \resumeItemListEnd

% Custom Neural Network Engine: Microgradient
\resumeProjectHeading
{\textbf{\href{https://github.com/kianis4/-neural-networks-zero-to-hero.}{Neural Network Engine: Micrograd}} $|$ \emph{Python, NumPy, PyTorch, Matplotlib, Graphviz, Machine learning}}{}
    \resumeItemListStart
        \resumeItem{Built a lightweight neural network framework from scratch with automatic differentiation and gradient-based optimization, achieving loss convergence below \textbf{0.02}, visualizing computational graphs to debug gradient flow.}
        \resumeItem{Reimplemented functionality in \textbf{PyTorch} to validate results and showcase industry-standard AI/ML proficiency.}
        % \resumeItem{Visualized computational graphs to debug gradient flow and parameter updates effectively.}
    \resumeItemListEnd
    
% Spotify Stats Viewer
\resumeProjectHeading
  {\textbf{\href{https://www.overload-pro.com/spotify}{Spotify Stats Viewer \& Instagram Post Viewer}} $|$ \emph{Next.js 13, Spotify API, Instagram API, Tailwind CSS, RESTful APIs}}{}
  \resumeItemListStart
        \resumeItem{Developed an interactive web app using \textbf{Spotify API} \& \textbf{Instagram API} to showcase user listening habits and social media content. Implemented OAuth 2.0 for authentication, optimized API calls to reduce latency, and designed a responsive \textbf{Spotify dashboard} with top tracks, artists, and user profiles. Built an \textbf{Instagram media carousel} with GSAP animations for a seamless user experience.}
    % \resumeItem{
    %   Built dynamic and responsive front-end interfaces using \textbf{Next.js 13} and \textbf{Tailwind CSS}, creating engaging user experiences with optimized performance and intuitive navigation.
    % }
  \resumeItemListEnd
    
\resumeSubHeadingListEnd

\end{document}