%-------------------------
% Resume in Latex
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{1pt}
    \small +1 289-788-8260 $|$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $|$
    \href{mailto:kianis4@mcmaster.ca}{\underline{kianis4@mcmaster.ca}} $|$ 
    \href{https://linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$
    \href{https://github.com/kianis4}{\underline{github.com/kianis4}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science in Computer Science CO-OP}{Sep. 2018 -- Nov 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software \& IT Systems Dev}{Aug. 2024 -- Present}
      {Burlington Training Centre}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Developed mobile applications at scale using \textbf{React Native}, \textbf{Swift}, \textbf{Kotlin}, \textbf{Java}, \textbf{Typescript}, and \textbf{Javascript} to optimize business operations, resulting in a \textbf{20\%} increase in operational efficiency, showcasing expertise in Java, Springboot, and API development.}
        \resumeItem{Implemented database optimization techniques like \textbf{Docker} and \textbf{Terraform} for seamless multi-environment deployments, reducing manual provisioning overhead and enhancing system performance, demonstrating proficiency in cloud platforms and CI/CD tools.}
        \resumeItem{Collaborated with distributed teams to integrate payment systems into the platform, \textbf{enhancing revenue by \$50,000} through optimized transaction fees, automated billing workflows, and leveraging SaaS principles, showcasing experience in financial services and payment platforms.}
        \resumeItem{Improved customer engagement by \textbf{30\%} through targeted notifications and rapid follow-ups by automating review requests with \textbf{AWS Lambda} and \textbf{RDS}, showcasing analytical skills and communication abilities.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Web Developer }{May 2021 -- Aug 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Proficient in building mobile and web applications at scale using technologies like \textbf{React Native}, \textbf{Swift}, \textbf{Kotlin}, \textbf{Java}, \textbf{Typescript}, and \textbf{JavaScript}, demonstrating adaptability and proficiency in modern tech stacks, including Springboot.}
        \resumeItem{Demonstrated expertise in database optimization and performance tuning, including optimizing \textbf{PostgreSQL} performance through indexing, caching, and query optimization, essential for large-scale systems, with a focus on API development and microservices.}
        \resumeItem{Skilled in building mobile and web applications at scale using technologies like \textbf{React Native}, \textbf{Swift}, \textbf{Kotlin}, \textbf{Java}, \textbf{Typescript}, and \textbf{JavaScript}, demonstrating proficiency in Agile methodologies, automation, and CI/CD tools for efficient development and deployment.}
        \resumeItem{Hands-on experience in implementing CI/CD pipelines to streamline rapid development and deployments, showcasing expertise in continuous integration and continuous deployment practices, crucial for mobile and web applications at scale, with a focus on unit testing.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
%-------------------------------------------%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{E\&S Solutions} $|$ \emph{Next.js, React, AWS, Docker, GitHub Actions}}{May 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Co-founded a software services venture delivering cloud-native, full-stack solutions for small businesses.}
            \resumeItem{Developed multiple scalable \textbf{TypeScript}-based applications using \textbf{Next.js} and \textbf{React}, deploying them on \textbf{AWS} (\textbf{EC2}, \textbf{S3}, \textbf{CloudFront}) and \textbf{Vercel} to achieve sub-second page loads, minimal latency, and availability.}
            \resumeItem{Automated complex data workflows using \textbf{Bash}, \textbf{Python}, and \textbf{Docker}, significantly reducing manual aggregation efforts by \textbf{80\%}, enhancing error handling and logging, and accelerating data-driven decision-making.}
            \resumeItem{Configured CI/CD pipelines with \textbf{GitHub Actions} and \textbf{Docker} to ensure rapid, reliable releases.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://www.skompxcel.com/}{\textbf{SKompXcel Academic Solutions}} $|$ \emph{Google Cloud, React, Python}}{Jan 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Founded a tutoring and mentorship platform for Computer Science and Software Engineering \textbf{20+} students.}
            \resumeItem{Architected the platform on \textbf{Google Cloud} (Compute Engine, Cloud Storage) for scalable hosting.}
            \resumeItem{Developed a \textbf{React} frontend with integrated scheduling and booking workflows to reduce administrative overhead.}
            \resumeItem{Leveraged \textbf{Python} for data reporting and performance tracking, increasing student success rates by \textbf{80\%}.}
          \resumeItemListEnd
          
      \resumeProjectHeading
            {\href{https://www.suleyman.io}{\textbf{Suley Fitness Portfolio}} $|$ \emph{Next.js, Tailwind CSS, React, Spotify API, Instagram API}}{2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a personal portfolio consolidating a blog, Spotify viewer, and Instagram viewer using \textbf{Next.js} and \textbf{Tailwind CSS}, showcasing my journey as a Developer, Personal Trainer, Tutor, and Martial Arts Instructor.}
            \resumeItem{Integrated external APIs with secure \textbf{OAuth 2.0} to fetch real-time data; view the blog at \href{https://www.suleyman.io/articles}{\textbf{suleyman.io/articles}}, the Spotify viewer at \href{https://www.suleyman.io/spotify}{\textbf{\textbf{suleyman.io/spotify}}}, and the Instagram viewer at \href{https://www.suleyman.io/insta}{\textbf{suleyman.io/insta}}.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://github.com/kianis4/Saftey-Net}{\textbf{Safety Net Crime Mapping}} $|$ \emph{Java, OpenCSV, LocationIQ API, Dijkstra’s Algorithm}}{2023}
          \resumeItemListStart
            \resumeItem{Developed a data-intensive \textbf{Java} application analyzing and visualizing over \textbf{4M+} NYPD arrest records, enabling user queries, borough-level crime filtering and real-time safety insights for tourists and real estate investors.}
            \resumeItem{Implemented \textbf{Dijkstra’s Algorithm} for real-time crime-weighted pathfinding, reducing geocoding lookup \textbf{40\%}.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd
% %-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, JavaScript, TypeScript, Python, C/C++} \\
     \textbf{Frameworks}{: Springboot, React, Next.js, Node.js, Flask, Django} \\
     \textbf{Developer Tools}{: Git, Docker, Kubernetes, GitHub Actions, Terraform, CI/CD Tools, Unit Testing} \\
     \textbf{Cloud \& Databases}{: AWS (EC2, S3, CloudFront, RDS), Google Cloud Platform, PostgreSQL, MongoDB} \\
    }}
 \end{itemize}%-------------------------------------------
\end{document}