%-------------------------
% Resume in Latex
% Author : Suleyman Kiani
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Suleyman Kiani} \\ \vspace{1pt}
    \small +1 289-788-8260 $|$ \href{mailto:suley.kiani@outlook.com}{\underline{suley.kiani@outlook.com}} $|$
    \href{mailto:kianis4@mcmaster.ca}{\underline{kianis4@mcmaster.ca}} $|$ 
    \href{https://linkedin.com/in/suleyman-kiani}{\underline{linkedin.com/in/suleyman-kiani}} $|$
    \href{https://github.com/kianis4}{\underline{github.com/kianis4}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {McMaster University}{Hamilton, ON}
      {Bachelor of Applied Science in Computer Science CO-OP}{Sep. 2018 -- Nov 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software \& IT Systems Dev}{Aug. 2024 -- Present}
      {Burlington Training Centre}{Burlington, ON}
      \resumeItemListStart
        \resumeItem{Built scalable mobile and web applications utilizing \textbf{React Native}, \textbf{Swift}, \textbf{Kotlin}, \textbf{Java}, \textbf{Typescript}, and \textbf{Ruby on Rails} to enhance deployment processes with \textbf{Kubernetes}, achieving a \textbf{40\%} decrease in release cycle times and enhanced system availability.}
        \resumeItem{Optimized end-to-end \textbf{CI/CD} workflows for mobile and web applications with \textbf{GitHub Actions}, \textbf{Jenkins}, and \textbf{Swift}, integrating automated testing, code quality checks, and seamless rollouts across diverse environments.}
        \resumeItem{Utilized \textbf{Terraform} to provision and manage AWS resources for mobile and web applications, enhancing provisioning processes for \textbf{Swift}, \textbf{Kotlin}, \textbf{Java}, \textbf{Typescript}, and \textbf{Ruby on Rails} components to boost scalability and ensure consistency.}
        \resumeItem{Implemented monitoring solutions for mobile and web applications with \textbf{Prometheus}, \textbf{Grafana}, and custom dashboards, enabling proactive performance monitoring, rapid incident response, and a \textbf{50\%} reduction in system downtime.}
      \resumeItemListEnd

    \resumeSubheading
      {Junior Web Developer }{May 2021 -- Aug 2022}
      {Giftcash Inc.}{Remote}
      \resumeItemListStart
        \resumeItem{Led the migration of a legacy \textbf{Python}/\textbf{Django} monolith to a \textbf{Node.js} serverless microservices architecture, achieving a \textbf{15\%} increase in scalability, showcasing adaptability to new technologies like Node.js and microservices, aligning with experience in SaaS development.}
        \resumeItem{Showcased expertise in database optimization by optimizing \textbf{PostgreSQL} performance through indexing, caching, and query optimization, reducing response times by \textbf{20\%} and enhancing data retrieval efficiency under high loads, aligning with experience in database optimization for large-scale systems and SaaS products.}
        \resumeItem{Automated gift card balance verifications across multiple platforms by developing efficient data extraction workflows using \textbf{Puppeteer} and \textbf{Axios} in an Agile environment, increasing operational efficiency by \textbf{25\%} and demonstrating proficiency in Agile processes, aligning with experience in SaaS development.}
        \resumeItem{Implemented efficient \textbf{CI/CD} pipelines with \textbf{Jenkins} and \textbf{GitHub Actions} to enable rapid, automated development cycles and seamless deployments across environments, aligning with experience in working with distributed teams, SaaS products, and large-scale systems.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{E\&S Solutions} $|$ \emph{Next.js, React, AWS, Docker, GitHub Actions}}{May 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Co-founded a software services venture delivering cloud-native, full-stack solutions for small businesses.}
            \resumeItem{Developed multiple scalable \textbf{TypeScript}-based applications using \textbf{Next.js} and \textbf{React}, deploying them on \textbf{AWS} (\textbf{EC2}, \textbf{S3}, \textbf{CloudFront}) and \textbf{Vercel} to achieve sub-second page loads, minimal latency, and availability.}
            \resumeItem{Automated complex data workflows using \textbf{Bash}, \textbf{Python}, and \textbf{Docker}, significantly reducing manual aggregation efforts by \textbf{80\%}, enhancing error handling and logging, and accelerating data-driven decision-making.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\href{https://www.skompxcel.com/}{\textbf{SKompXcel Academic Solutions}} $|$ \emph{Google Cloud, React, Python}}{Jan 2024 -- Present}
          \resumeItemListStart
            \resumeItem{Founded a tutoring and mentorship platform for Computer Science and Software Engineering \textbf{20+} students.}
            \resumeItem{Architected the platform on \textbf{Google Cloud} (Compute Engine, Cloud Storage) for scalable hosting.}
          \resumeItemListEnd
          
      \resumeProjectHeading
            {\href{https://www.suleyman.io}{\textbf{Suley Fitness Portfolio}} $|$ \emph{Next.js, Tailwind CSS, React, Spotify API, Instagram API}}{2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a personal portfolio consolidating a blog, Spotify viewer, and Instagram viewer using \textbf{Next.js} and \textbf{Tailwind CSS}, showcasing my journey as a Developer, Personal Trainer, Tutor, and Martial Arts Instructor.}
            \resumeItem{Integrated external APIs with secure \textbf{OAuth 2.0} to fetch real-time data; view the blog at \href{https://www.suleyman.io/articles}{\textbf{suleyman.io/articles}}, the Spotify viewer at \href{https://www.suleyman.io/spotify}{\textbf{\textbf{suleyman.io/spotify}}}, and the Instagram viewer at \href{https://www.suleyman.io/insta}{\textbf{suleyman.io/insta}}.}
          \resumeItemListEnd
    \resumeProjectHeading
        {\href{https://github.com/kianis4/load-balancer}{\textbf{Load Balancer System}} $|$ \emph{Python, Sockets, Multi-threading, Logging}}{2023}
        \resumeItemListStart
          \resumeItem{Implemented a multi-threaded load balancer in \textbf{Python} to efficiently distribute incoming client requests across multiple backend servers using both \textbf{Round-Robin} and \textbf{Least Connections} strategies.}
          \resumeItem{Engineered robust fault tolerance and real-time health monitoring, automatically detecting server failures and reintegrating recovered servers to maintain high availability.}
          % \resumeItem{Integrated comprehensive logging and performance tracking to monitor request flow, response times, and server status, ensuring rapid troubleshooting and system optimization.}
        \resumeItemListEnd

    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Scripting}{: Python, JavaScript, TypeScript, Java, Bash, PowerShell} \\
     \textbf{DevOps Tools}{: Git, Docker, Kubernetes, GitHub Actions, Terraform, Jenkins, Ansible} \\
     \textbf{Cloud \& Databases}{: AWS (EC2, S3, CloudFront, RDS, Lambda, EKS), GCP, PostgreSQL, MongoDB} \\
     \textbf{Monitoring \& Automation}{: Prometheus, Grafana, ELK Stack, Nagios, Selenium}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
